Dynamics of innovation in stigmergic collectives

### 2023-06-23 LaTeX/draft.tex
TriggerFound
ErrorFound
rwdPlotsClear

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{./figs/schematic.pdf}\label{fig:schm1}
    \caption{Schematic of setup}
\end{figure*}

@@

= 2\int_0^\sigma \mu \sqrt{\sigma^2-\zeta^2} \ \d \zeta/\psi(s^*-\zeta)$. We can now calculate the value function, $v_{\rm OU}(\r, \theta)$ as

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{./figs/fig1.pdf}\label{fig:schm1}
    \caption{Schematic of setup}
\end{figure*}

@@

= 2\int_0^\sigma \mu \sqrt{\sigma^2-\zeta^2} \ \d \zeta/\sqrt{\psi(s^*-\zeta)}$. We can now calculate the value function, $v_{\rm OU}(\r, \theta)$ as
\textbf{***This cannot be done because trajectories have to be conditioned on the previous step if intersection at a particular location has to be accounted.***}
